Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-05-31 ms.tex
reference is added

Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
It has been known that Jupiter emits radio emission from the radiation belt and auroral region due to the acceleration of the plasmas. \memoYF{?}.
Potentially, large exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons. 
Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001, griesmeier2007a, griesmeier2007b, hallinan_et_al2013, noyola2014}.
Although the search for these radio signatures are being conducted, there is no clear detection claimed so far, while some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013}.

@@

Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} \memoYF{check!} (see \citet{griesmeier2004} or \citet{christensen2010} for the summary). 
%
They are compared with numerical simulations in \citet{christensen2010}. We employ the following relationship from \citet{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space \memoYF{describe in more detail}:
%%%%%%%%%% 
\begin{equation}
B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
\end{equation}
%%%%%%%%%%
where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
Magnetic field of planets are estimated by scaling Jovian magnetic field $B_J \sim 10$~G by equation (\ref{eq:Bscaling}).

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}. 
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=700\,\mbox{kg/m}^3$ \memoYF{cite something!}. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$.

The convected heat flux, $q_c$, is estimated by dividing the time-dependent net planetary luminosity by the surface area of the core region ($4\pi r_c^2$). 
The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
%%%%%%%%%%
\begin{equation}
L \sim {10^{-8} L_\odot} \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{1~M_J} \right)^{2.64} \, .
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
\memoYF{Burrows et al. 2001 says $10^{-9} L_\odot $, but it looks to me like it is actually $10^{-8} L_\odot $}. 
We estimate the convected heat flux by dividing this energy flux by the surface area of the core region, i.e., $4 \pi r_c^2$.

\memoYF{I am not sure if the following paragraph is needed.}
There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
In particular, \citet{griesmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
%%%%%%%%%% 
\begin{equation}
\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
\end{equation}
%%%%%%%%%%
where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$.

%
Unlike canonical hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants. Without no physical insights of the typical spin rate, we could assume that of Jupiter: $\omega = 9.925$ [hr].

@@

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griesmeier2007b}. 
This is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
\end{eqnarray}
%%%
where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
%
In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
Because... \memoYF{I want to justify not to consider the magnetic case.}, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.

@@

The maximum radio emission we can expect to observe is limited by the plasma cut-off frequency of the stellar wind in the vicinity of the planets. 
For a planet with the same magnetic moment as Jupiter, the maximum radio emission from the planets which can penetrate through the surrounding plasma is $\sim 10^{-3}$ Jy or $\sim 10^{-5}$ Jy at 10 pc and 100 pc, respectively. 
\memoYF{comment on observability!!}

>>>>

Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
It has been known that Jupiter emits radio emission from the radiation belt and auroral region due to cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
Potentially, large exoplanets can also emit radio waves through the similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons. 
Radio emissions from exoplanets have been estimated taking account of several possible processes, based on the empirical scaling of the radio intensity with the solar wind flux \citep{zarka2001, griesmeier2007a, griesmeier2007b, hallinan_et_al2013, noyola2014}.
Although the search for these radio signatures are being conducted, there is no clear detection claimed so far, while some indications were obtained \memoYF{?} \citep{lecavelier_et_al2013}.

@@

Several relationships have been proposed so far \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006} %\memoYF{check!}
(see \citet{griesmeier2004} or \citet{christensen2010} for the summary). 
%
They are compared with numerical simulations in \citet{christensen2010}. We employ the following relationship from \citet{christensen2006}, which was found to be in a good agreement with the numerical experiments over a wide parameter space 
%\memoYF{describe in more detail}:
%%%%%%%%%% 
\begin{equation}
B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
\end{equation}
%%%%%%%%%%
where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
Magnetic field of planets are estimated by scaling Jovian magnetic field $B_J \sim 10$~G by equation (\ref{eq:Bscaling}).

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of planets. 
In this paper, we consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, because the numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}. 
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006}. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
%In the case of Jupiter, $r_{c,\,J} = 0.85 R_{\rm J}$.

The convected heat flux, $q_c$, is estimated by dividing the time-dependent net planetary luminosity by the surface area of the core region ($4\pi r_c^2$). 
The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
%%%%%%%%%%
\begin{equation}
L \sim 10^{-8} L_\odot \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{1~M_J} \right)^{2.64} \, .
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
We estimate the convected heat flux by dividing this luminosity by the surface area of the core region, i.e., $4 \pi r_c^2$.

%\memoYF{I am not sure if the following paragraph is needed.}
%There also exist several other scaling relations proposed so far, which is compared in \citet{christensen2010}. 
%In particular, \citet{griesmeier2004} estimated radio emission of discovered exoplanets based on the following scaling relationship: 
%%%%%%%%%% 
%\begin{equation}
%\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
%\end{equation}
%%%%%%%%%%
%where $\omega $ is the spin angular velocity and $\sigma $ is the conductivity of the ``dynamo region'', which is assumed to be same as Jupiter. 
%The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. 
%
%Unlike canonical hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants. Without no physical insights of the typical spin rate, we could assume that of Jupiter: $\omega = 9.925$ [hr].

@@

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission with the input energy from stellar wind, in the same manner as \citet{griesmeier2007b}. 
This is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy or the magnetic energy of the solar wind \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag},
\end{eqnarray}
%%%
where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
%
In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both.

In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.

Magnetic field of evolved stars are not well constrained \citep{konstantinova2010}. 
If the correlation with input magnetic energy is the case, the radio emission would be rather weaker than the Jupiter, because the magnetic field of evolved stars

@@

The maximum radio emission we can expect to observe is limited by the plasma cut-off frequency of the stellar wind in the vicinity of the planets. 
For a planet with the same magnetic moment as Jupiter, the maximum radio emission from the planets which can penetrate through the surrounding plasma is $\sim 10^{-3}$ Jy or $\sim 10^{-5}$ Jy at 10 pc and 100 pc, respectively. 
\memoYF{comment on observability...}
